Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-08-31 paper/ms.tex
update ms

In both models, the corotation radius is the location at which matter
concentrates.  The empirical basis for this is that
the sharp CR features are superposed over smooth, quasi-sinusoidal
starspot profiles.  The theoretical importance of the corotation
radius has been discussed in studies of magnetic rotators
\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,2005ApJ...634.1214L}.
%
%including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
%massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
%Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
%
In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
> \rho v^2 /2$), matter is dragged along with the field lines.  The
tendency for charged gas or dust to become trapped at corotation is
then tied to how of the four relevant forces -- gravity, Lorentz,
inertial Coriolis, and inertial centrifugal -- the Lorentz and
Coriolis only act perpendicular to field lines, while gravity and the
centrifugal force are in balance at $R_{\rm c}$ \citep[e.g.][their
Section~2]{2005MNRAS.357..251T}.  Another way to phrase this statement
is that there is a local minimum in the effective potential of the
corotating frame; given a flow from the either the star or from a
tenuous accretion disk, this local potential minimum enables material
to build up \citep{2005MNRAS.357..251T}.

@@

\subsubsection{What is a prominence?}
The prominence idea is based on an analogy with quiescent
prominences/filaments in the solar corona that last as long as a few
weeks \citep[see][]{2015ASSL..415.....V}.  In the context of the Sun,
a prominence is a clump of cold, partially ionized hydrogen viewed in
emission against the dark backdrop of space.  A filament is the same
clump of plasma, but viewed in absorption against the solar disk.  In
an extrasolar context, spectroscopic detections of transient Balmer-
and resonance-line absorption seen for stars such as AB~Dor and
Speedy~Mic
\citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
have been interpreted as prominences that scatter a star's
chromospheric emission \citep[see][]{1989MNRAS.238..657C}.  The
short-term mechanical stability of such gas configurations is
theoretically plausible for such stars
\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}.   To our best
knowledge, this class of spectroscopic observation also has no viable
alternative explanations.

@@

      dur}$ (Figure~\ref{fig:cqvs}).  Such dips are often superposed

@@

      only viable explanation for the sharp dips being superposed on
      the quasi-sinusoidal signals is that clumps of circumstellar
      material are corotating with the star.  Assuming that the longer
      dips have the same physical origin as the shortest dips, the
      transiting material must therefore also be capable of having
      effective sizes comparable to the star.

>>>>

In both models, the corotation radius is the location at which matter
concentrates.  The empirical basis for this is that
the sharp CR features are superposed over smooth, quasi-sinusoidal
starspot profiles.  The theoretical importance of the corotation
radius has been discussed in studies of magnetic rotators
\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,2005ApJ...634.1214L}.
%
%including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
%massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
%Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
%
In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
> \rho v^2 /2$), matter is dragged along with the field lines.  The
tendency for charged gas or dust to become trapped at corotation is
then tied to how of the four relevant forces -- gravity, Lorentz,
inertial Coriolis, and inertial centrifugal -- the Lorentz and
Coriolis only act perpendicular to field lines, while gravity and the
centrifugal force are in balance at $R_{\rm c}$ \citep[e.g.][their
Section~2]{2005MNRAS.357..251T}.  Another way to phrase this statement
is that there is a local minimum in the effective potential of the
corotating frame; given a flow from either the star or from a
tenuous accretion disk, this local potential minimum enables material
to build up \citep{2005MNRAS.357..251T}.

@@

\subsubsection{What is a prominence?}
The prominence idea is based on an analogy with quiescent
prominences/filaments in the solar corona that last as long as a few
weeks \citep[see][]{2015ASSL..415.....V}.  In the context of the Sun,
a prominence is a clump of cold, partially ionized hydrogen viewed in
emission against the dark backdrop of space.  A filament is the same
clump of plasma, but viewed in absorption against the solar disk.  In
an extrasolar context, spectroscopic detections of transient Balmer-
and resonance-line absorption seen for stars such as AB~Dor and
Speedy~Mic
\citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
have been interpreted as prominences that scatter a star's
chromospheric emission \citep[see][]{1989MNRAS.238..657C}.  The
short-term mechanical stability of such gas configurations is
theoretically plausible for rapidly rotating stars
\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}.   To our best
knowledge, this class of spectroscopic observation also has no viable
alternative explanations.

@@

      dur}$ (Figure~\ref{fig:cqvs}).  The dips are often superposed

@@

      only viable explanation currently known for the sharp dips being superposed on
      the quasi-sinusoidal signals is that concentrations (``clumps'')
      of circumstellar material are corotating with the star.
      Assuming that the longer dips have the same physical origin as
      the shortest dips, the transiting material must therefore also
      be capable of having effective sizes comparable to the star.
